---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# organiser 


## Overview  

`organiser` is an R package designed to streamline project setup and management. It provides functions to create a standardized project structure, manage dependencies, and maintain a reproducible workflow.  


### Key Functions  

- `organise()` – Creates a structured project directory with predefined subfolders.  
- `setup_renv()` – Initializes an **renv** environment for dependency management.  
- `add_module()` – Adds modular components for better project organization.  
- `load_config()` – Loads configuration settings to maintain consistency.  
- `validate_project()` – Ensures the project structure follows best practices.  

These functions enhance **reproducibility, scalability, and organization** in R projects. Learn more in `vignette("organiser")`.  

## Installation

```{r, eval = FALSE}
library('devtools')
install_github('clementrx/organiser')
```

## Usage

```{r, eval = FALSE, message = FALSE}
library(organiser)

organise("my_project")
```

## Getting help

If you encounter a clear bug, questions, please file an issue with a minimal reproducible example on [GitHub](https://github.com/organiser/issues). 


