---
title: "Introduction to organiser"
author: "Clément Rieux"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to organiser}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The `organiser` package helps you create structured R projects easily. It automatically generates project folders, example files, a Quarto report, and sets up `renv` for package management.

## Installation

To install `organiser` from GitHub:

```{r, eval=FALSE}
# Install devtools if not already installed
install.packages("devtools")

# Install organiser package
devtools::install_github("your_github_username/organiser")
```

## Creating a New Project

Use the `organise()` function to create a new R project:

```{r, eval=FALSE}
library(organiser)

# Create a project named "my_project"
organise("my_project")
```

This will create the following structure:

```
my_project/
│── install.R
│── main.R
│── functions/
│   ├── example_function.R
│── scripts/
│   ├── example_script.R
│── tests/
│   ├── test_example.R
│── outputs/
│── config/
│   ├── config.yml
│── report/
│   ├── report.qmd
│── README.md
```

## Customizing Your Project

- **Edit `main.R`** to load additional libraries.
- **Modify `report.qmd`** for your project documentation.
- **Use `renv`** to manage package dependencies.

## Next Steps

- Explore the example functions and scripts.
- Extend the project with additional scripts and configurations.
- Run `renv::snapshot()` to save package dependencies.

Happy coding! 🚀
